\documentclass[letterpaper, 10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}

\begin{document}

\title{\vspace{-2cm}Kardam Soni}
\date{}
\maketitle

\section*{Contact}
\begin{tabular}{l l}
Location: & Lowell, MA \\
Phone: & 978.319.0932 \\
Email: & kardam.soni@gmail.com \\
LinkedIn: & linkedin.com/in/kardam-soni-76527192/
\end{tabular}

\section*{Summary}
Highly motivated, dedicated, and team-oriented DevOps engineer with 10+ years of experience in Defense Software development and Ops, seeking a leadership role that allows the ability to demonstrate abilities in strategic design and implementation of a comprehensive IT strategy for a mission-driven enterprise.

\section*{Education}
\textbf{University of Massachusetts}, Lowell, MA \\
Bachelor of Science: Computer Engineer \hfill 2010–2014

\section*{Professional Dev Experience}
\textbf{Sr DevOps ENGINEER | SigmaDefense} \hfill May 2020 – Present
\begin{itemize}
    \item Platform Engineer and CI/CD Lead for the tactical PaaS | Forge Software Factory
    \item Architecting and developing a HA'd (Highly Available) PaaS (Platform as a Service) running RKE2 (Rancher Kubernetes Engine) with Identity Manager and Ldap services, deployed via IaC (Infrastructure as Code) using languages such as Ansible, Packer, Helm charts, and Terraform on different IaaS (Infrastructure as a Service) including AWS, Azure, and VSphere on-prem.
    \item Architected solutions to migrate Development Efforts to deploy the PaaS on cloud from an AWS Cloud environment to a managed AWS Cloud environment with Infrastructure as Code.
    \item Led efforts to design and implement CI/CD Pipelines on Jenkins and migrate the pipelines to Gitlab and ultimately Gitlab Ultimate and Terraform enterprise.
    \item Implemented Cyber Security Technical Implementation at all levels of the app including OS, Network, Kubernetes, RKE2, Rancher, Docker, Containers, and all the Guidelines provided by the Department Information System Agency.
    \item Researched and Deployed cluster management apps like Flux, Zarf, and other platform services like HashiCorp Vault, Certmanager, Rancher, OPA Gatekeeper, ELK Stack, and configuring Istio via Ansible and GitOps.
    \item Deployed custom Apps using Helm charts and configured them to work with existing platform services via GitOps.
    \item Managed a team of four Engineers, including PTO requisitions, timecards, and yearly and regular performance evaluations and check-ins. Mentored two software engineers and participated in technical assessment interviews to join the team.
\end{itemize}

\textbf{DevOps Engineer | ASRC Federal Mission Solutions} \hfill May 2020 – June 2020
\begin{itemize}
    \item Helped in deploying Openshift (DevOps Cluster Manager) installation and configuration using Ansible.
    \item Containerized Development Jenkins Service, GitLab Service, and SonarQube Service.
    \item Wrote Ansible roles to deploy Jenkins, Bitbucket, and Confluence in Openshift to set up DevSecOps Environment.
\end{itemize}

\textbf{Senior Software Engineer | Lockheed Martin Space} \hfill Jan 2019 – May 2020
\begin{itemize}
    \item Software Engineer | Advance Extremely High-Frequency Satellite
    \item Designed Crypto Planning Application using C# and MVVM framework to work with SQL server and WPF to facilitate Air Force's use of Cryptographic Key Management.
    \item Researched and integrated a new FTP Library in C++ codebase to replace Server-based file transfer, saving 3.6+ Million dollars in Software Architecture upgrade.
    \item Developed and integrated new features to meet contractual obligations and customer satisfaction.
    \item Led DevOps efforts to build CI/CD automation with nightly builds and deployments.
    \item Redesigned Monolithic Apps into small Microservice architecture to support faster builds and independent development.
\end{itemize}

\textbf{Software Engineer | Raytheon Integrated Defense Systems} \hfill June 2014 – Dec 2019
\begin{itemize}
    \item Software Engineer | Quarter Early Warning Radar \hfill Sep 2019 – Apr 2020
    \item Developed code in C++ in a scaled agile environment to develop software for Quarter's Early Warning Radar System.
    \item OPS: Developed scripts to make Secure Stig'd Live RedHat Images to be used for deployment.
    \item OPS: Developed scripts to package dependent libraries and configuration changes into RPM packages.
    \item Software Engineer | Zumwalt Class Destroyer \hfill Sep 2019 – Apr 2020
    \item Developed code in C++ and Java for a distributed system running on 36 embedded machines and 12 servers to process 300,000+ sensor values in real-time using various Network protocols like CORBA and DDS RTI.
    \item Debugged Software, Hardware, Oracle, and Networking Issues, with Wireshark, GDB, and parsing System Loggers.
    \item OPS: Part of the installation team, to install the software on 300 plus nodes using TFTP and Remote RPM installation.
\end{itemize}

\textbf{Summer Intern | Sonus Networking} \hfill May 2012 – Aug 2013
\begin{itemize}
    \item Used Clearcase and ClearQuest in Unix Environment to merge hotfixes and build software.
\end{itemize}

\textbf{Part-Time Intern | X-Rite Pantone} \hfill June 2014 – Dec 2019
\begin{itemize}
    \item Developed and executed test cases to test software.
\end{itemize}

\textbf{Summer Intern | MKS} \hfill June 2014 – Dec 2019
\begin{itemize}
    \item Collaborated with Dell Services to assist email client migration for Lotus Notes to Outlook.
\end{itemize}

\end{document}
